\documentclass[a4paper,11pt]{article}

%\usepackage[margin=0.05in]{geometry}

%A Few Useful Packages
\usepackage{marvosym}
\usepackage{fontspec} 					%for loading fonts
\usepackage{enumitem}
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[big]{layaureo} 				%better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section

%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.1,0.2}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
\setlist[itemize]{itemsep=-7	pt, topsep=-6pt}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{
\setmainfont[
SmallCapsFont = Fontin-SmallCaps.otf,
BoldFont = Fontin-Bold.otf,
ItalicFont = Fontin-Italic.otf
]
{Fontin.otf}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{0pt}{0pt}

\geometry{top=0.4in,left=0.55in,bottom=0.4in,right=0.55in}

\begin{document}

\pagestyle{empty} % non-numbered pages

%--------------------TITLE-----------------------
\par{\centering{\Huge Mark Lalor}\par}
\begin{center}
\href{mailto:markwlalor@gmail.com}{markwlalor@gmail.com} • Cleveland, OH \\
\href{https://linkedin.com/in/marklalor/}{linkedin.com/in/marklalor} • \href{http://github.com/marklalor}{github.com/marklalor}
\end{center}

%--------------------SECTIONS--------------------

% -------------- EDUCATION--- ----------
\section{Education}
\begin{tabular}{lp{15cm}}
\textbf{Case Western Reserve University} & \textsc{Sep} 2016 -- \textsc{Dec} 2019 \\
Bachelor of Science in Computer Science &  \textsc{GPA}: 3.825\\
\end{tabular} \\
\begin{tabular}{rp{14cm}}
\textsc{Current Classes}: & \footnotesize{Computer Security, Applied Graph Theory, Software Defined Networks, Databases, Number Theory} \\
\textsc{Completed Classes}: & \footnotesize{Algorithms, Data Structures, Artificial Intelligence, Computer Networks, Programming Language Concepts, Operating Systems and Concurrent Programming}
\end{tabular}
\\
% ---------- WORK EXPERIENCE ----------
\section{Work Experience}
\textsc{Research Assistant} | Case School of Engineering, \href{http://engr.case.edu/rabinovich_michael/}{Rabinovich} Lab \\
\textsc{Sep 2018 – Present} | Cleveland, OH
\begin{itemize}
	\item Conducting a measurement of the adoption of the EDNS Client Subnet (ECS) extension to DNS.
	\item Assessing the utility of the ECS extension for distributed platforms scanning.
\end{itemize}
\vskip 3mm
\textsc{Software Engineer Intern} | MIM Software \\
\textsc{May 2018 – Aug 2018} | Beachwood, OH
\begin{itemize}
	\item Implemented multi-factor authentication for an existing cloud software suite.
	\item Added options for time-based one-time passwords, SMS messages, and backup codes.
	\item Created new server-side services and added new HTTP endpoints for clients.
\end{itemize}
\vskip 3mm
\textsc{Teaching Assistant (Intro to Java)} | Case School of Engineering \\
 \textsc{Sep 2017 – Dec 2017} | Cleveland, OH
 \begin{itemize}
	 \item	Led two lab sections per week, assisting students completing the assignments.
	 \item Held a weekly office hour with a mini-lesson and project discussion.
	 \item Graded and provided feedback on lab assignments and projects.
 \end{itemize}
 \vskip 3mm
 \textsc{Software Engineer Intern} | MIM Software \\
 \textsc{May 2017 – Aug 2017} | Beachwood, OH
 \begin{itemize}
	\item Created new viewer/editor for DICOM (medical image) files that interfaces with main software.
	\item Maintained existing software components through version control and code review.
 \end{itemize}
\section{Leadership and Clubs}
\begin{itemize}[noitemsep]
	\item \emph{\href{http://hacsoc.org}{Hacker Society} Maintainer}: Organize weekly tech talks on campus. Reach out to current students as well as industry professionals and alumni to give talks.
	\item \emph{CWRU ACM Secretary}: Plan, manage, and volunteer for events that teach and support CS on campus. Provide guidance in regards to classes, the computer science department, and careers.
	\item \emph{Vietnamese Student Association}: Promote Vietnamese culture on campus and the Cleveland community by helping with events. Volunteer as a mentor for a mentor/mentee program for new students.
\end{itemize}
\section{Skills}
\textsc{Programming Languages}:
\begin{tabular}[noitemsep]{ll}
	\textsc{Proficient}: & Java, Python \\
	\textsc{Experience}: & Scala, SQL, C, HTML, CSS, Javascript \\
\end{tabular}

\textsc{Software and Frameworks}: Linux, Git, Mercurial, JUnit, Guava, Swing, Google Cloud Platform, Nginx, Redis
\section{Projects}
\begin{itemize}
    \item \emph{\href{https://github.com/marklalor/PLCInterpreter}{PLC Interpreter}}: Interpreter for a Java-like programming language with constructs such as objects, polymorphism, loops, recursion, and nested functions. Project in Programming Language Concepts.
    \item \emph{\href{https://github.com/marklalor/clanvas}{Clanvas}}: Command-line client for the Canvas learning management system. Uses the Canvas HTTP API to generate grade summaries, list assignments, and download course files.
    \item \emph{\href{https://github.com/ucfopen/canvasapi}{Canvasapi} and \href{https://github.com/python-cmd2/cmd2}{Cmd2}}: Open-source libraries used in Clanvas which I contribute back to.
    \item \emph{\href{https://github.com/marklalor/Tutoring-Log}{TutoringLog}}: Google App Engine application to track/verify student tutoring sessions. Successfully used by 100-student math honor society at high school.
\end{itemize}

\end{document}
